---
title: "Untitled"
author: "Winnie the Pooh"
date: "1/24/2019"
output: html_document
lang: ru-RU
editor_options: 
  chunk_output_type: console
---

Hi everyone!

Привет всем!

# Introduction

In this **important research** _we will_...

# Main part

\[
r = \sqrt{x^2 + y^2}
\]

Here is the list:

1. First point
1. Second point
1. Third point

Code - Insert chunk

```{r, message=FALSE, echo=TRUE}
library(tidyverse) # data manipulations
library(skimr) # summary statistics
library(texreg) # beautiful tables to compare models
library(lmtest) # tests in linear models
library(estimatr) # regression with robust se
```

Let's estimate some OLS models with robust standart errors and make a report.

```{r}
model_a = lm_robust(data = diamonds, price ~ carat)
model_b = lm_robust(data = diamonds, price ~ carat + x + y + z + table)
```

Each model can be summarized separately:
```{r}
summary(model_b)
```
Create one table summarizing results from both regressions:
```{r, results='asis'}
htmlreg(list(model_a, model_b))
```

No problem with plots
```{r}
qplot(data = diamonds, x = carat, y = price, color = color) + 
  facet_wrap(~ cut) + 
  labs(x = "Weight of a diamond in carats",
       y = "Price in dollars",
       title = "Price of 50000+ diamonds")
```

Let's download russian monthly wages:
```{r}
library(sophisthse)
data = sophisthse("WAG_M")
```

Look at what we have downloaded:
```{r}
head(data)
```

Let's do forecasting
```{r}
library(forecast)
```

Let's use auto-arima model:
```{r}
y = data[, 1] # select first column!
model_arima = auto.arima(y)
model_arima
```

Do forecasts
```{r}
future_arima = forecast(model_arima, h = 24)
future_arima
autoplot(future_arima)
```

Let's use TBATS model
```{r}
model_tbats = tbats(y)
model_tbats
future_tbats = forecast(model_tbats, h = 24)
future_tbats
autoplot(future_tbats)
```

Let's beautify a table with forecasts!
```{r}
library(huxtable)
huxtable(future_tbats)
```










