Loading all necessary libraries...
```{r}
library(ggplot2)
library(lmtest)
library(foreign)
```

`ggplot2` for beautiful graphs, `lmtest` for various test (Wald test, LR test etc), `foreign` for reading data in spss, stata and other ugly formats.


First of all we set working directory. There R will search for files:
```{r}
setwd("~/science/econometrix/em301/sem_01_logit_plita/")
```

Now we load the dataset from the file `mesto_jenshini.dta` into the data frame `h`.  
```{r}
h <- read.dta("mesto_jenshini.dta")
```

Let's check whether everything is loaded correctly:
```{r}
head(h)
summary(h)
```

Let's look on some specific variables. Income. Probably year income divided by family size.
```{r}
summary(h$adjinc)
```

Let's make some simple graphs
```{r}
hist(h$agree)
```

Graphical analysis before estimation...


Let's estimate logit model
```{r}
m1 <- glm(agree~age+adjinc+nsibs,
          data=h,
          family=binomial(link="logit"))
summary(m1)
```



Let's make predictions. First, we create a new data frame:
```{r}
new <- data.frame(age=c(20,24),
                  adjinc=c(16000,4000),
                  nsibs=c(2,5))
new
```

Now we predict probability for these additional observations
```{r}
predict(m1,new,type="response")
```

Constructing the confidence interval for these new observations:
```{r}
forecast <- predict(m1,new,type="response",se.fit=TRUE)
new$hat.p <- forecast$fit
new$hat.p.se <- forecast$se.fit
z.crit <- qnorm(0.975)
new$ci.left <- new$hat.p - z.crit * new$hat.p.se
new$ci.right <- new$hat.p + z.crit * new$hat.p.se
new
```

Binary prediction. Best binary prediction?

Graphical analysis after estimation...

Likelihood ratio, LR-test, Тест отношения правдоподобия
```{r}
m2 <- glm(agree~age+age2+adjinc+nsibs,
          data=h,
          family=binomial(link="logit"))
lrtest(m1,m2)
```

Lagrange multiplier test, LM-test, тест множителей Лагранжа (? by hands)

Wald-test, Тест Вальда
```{r}
waldtest(m1,m2,test="Chisq")
```


